Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials

### 2012-12-03 paper.tex
Integrated most of Ibs and Oles corrections

Already early theoretical descriptions of the oscillatory behavior, on even very simple catalytic systems, noticed that oscillations can occur in many systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}). The details of the oscillations are, however, extremely specific to the given system and it can thus be difficult to predict how and if a given system will oscillate. Oscillations in catalytic systems can be quite complex and the parameter space can be very large. In the system investigated in this paper oscillations could be dependent on morphological parameters of the nanoparticles such as size, shape and exposed facets. Also, the oxidation state and possible pollution on the surface could have impact on the system. More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will also influence the systems ability to show kinetic oscillations.

@@

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles. However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected. Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nanoparticles. However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the exact particle morphology.

>>>>

Already early theoretical descriptions of the oscillatory behavior, even on very simple catalytic systems, noticed that oscillations can occur in many systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}). The details of the oscillations are, however, extremely specific to the given system and it can thus be difficult to predict how and if a given system will oscillate. Oscillations in catalytic systems can be quite complex and the parameter space can be very large. In the system investigated in this paper oscillations could be dependent on morphological parameters of the nanoparticles such as size, shape and exposed facets. Also, the oxidation state and possible pollution on the surface could have impact on the system. More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor may also influence the systems ability to show kinetic oscillations.

@@

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles. However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected. Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nanoparticles. However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the size.

### 2012-12-03 supplementary.tex
Integrated most of Ibs and Oles corrections

\section{TEM Imaging}
!!! It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement. However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction. This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding, which cannot be reversed and thus the lid can only be removed by mechanically breaking the device. Images of the as-deposited particles are on the other hand quite easy to acquire by depositing on a substrate more suitable for TEM under conditions identical to those of the deposition into the $\mu$-reactor. Such an image is shown in Figure~\ref{fgr:gas_dependence}. Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.!!!!
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{3nm_Pt_on_SiO2.png}
  \caption{Image of as-deposited nanoparticles deposited on a thin substrate of SiO$_2$.}
  \label{fgr:tem_3nm}
\end{figure}

>>>>

\section{TEM Imaging}
It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement. However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction. This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding, which cannot be reversed and thus the lid can only be removed by mechanically breaking the device. Images of the as-deposited particles are on the other hand quite easy to acquire by depositing on a substrate more suitable for TEM under conditions identical to those of the deposition into the $\mu$-reactor. Such an image is shown in Figure~\ref{fgr:gas_dependence}. Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{3nm_Pt_on_SiO2.png}
  \caption{Image of as-deposited nanoparticles deposited on a thin substrate of SiO$_2$.}
  \label{fgr:tem_3nm}
\end{figure}
